\section*{Simulation Findings}
\addcontentsline{toc}{section}{Simulation Findings}

\subsection*{13.1.1.Understanding Brian2 Monitors}
\addcontentsline{toc}{subsection}{Understanding Brian2 Monitors}

\textbf{For each of the four subpopulations, find the variable name of the corresponding NeuronGroup.} \\

The four subpopulations are \textbf{inhib\_pop} which is the inhibitory population, \textbf{excit\_pop\_A}, \textbf{excit\_pop\_B} and \textbf{excit\_pop\_Z} which are the excitatory population. \\

\textbf{Each NeuronGroup is monitored with a PopulationRateMonitor, a SpikeMonitor, and a StateMonitor. Find the variable names for those monitors. Have a look at the Brian2 documentation if you are not familiar with the concept of monitors.}\\

For the inhibitory population, the PopulationRateMonitor, SpikeMonitor and StateMonitor is \textbf{rate\_monitor\_inhib,spike\_monitor\_inhib, voltage\_monitor\_inhib}.\\
For the excitatory populations, the PopulationRateMonitor, SpikeMonitor and StateMonitor are \textbf{rate\_monitor\_A, spike\_monitor\_A, voltage\_monitor\_A} ,  \textbf{rate\_monitor\_B, spike\_monitor\_B, voltage\_monitor\_B} and \textbf{rate\_monitor\_Z, spike\_monitor\_Z, voltage\_monitor\_Z}.\\

\textbf{Which state variable of the neurons is recorded by the StateMonitor?}\\

The voltage "v" is being recorded.

\subsection*{13.2 Stimulating the decision making circuit}
\addcontentsline{toc}{subsection}{Stimulating the decision making circuit}

\textbf{express the difference $ \mu_{left} $ - $ \mu_{right} $ in terms of $ \mu_{0}$ and c}\\

The difference is $ \mu_{0}*c$.\\

\noindent \textbf{Find the distribution of the difference $ v_{left}- v_{right} $.}\\

$ v_{left}$ $\approx$ N($ \mu_{left} $, $ \sigma^{2} $)\\
\indent $ v_{right}$ $\approx$ N($ \mu_{right} $, $ \sigma^{2} $)\\

\indent $v_{left}$ - $v_{right}$ $\approx$ $v_{left}$ + (-1) $ v_{right}$ 

$ \approx $ N($\mu_{left} - \mu_{right}$, 0)\\

\noindent \textbf{Find the default values of of $ \mu_{0}$ and $ \sigma^{2}$}\\

\indent $\mu_{0}$ is 160 Hz and $ \sigma^{2}$ = is 20 Hz.\\

\noindent \textbf{What are the mean firing rates for c =-0.2}

\indent  $ \mu_{left}$ is 64 Hz. $ \mu_right{right}$ is 96 Hz.\\

\noindent \textbf{For c= -0.2, how does the difference $ \ \mu_{left} - \mu_{right} $ compare to the variance of v_{left} .} 






